Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Polish "expecting exceptions"

\noindent Or we may expect that a value should satisfies some
predicate.

@@

HUnit does not provide any versatile mechanism to state that an action
should throw an exception.  So we propose a combinator for that.

@@

\noindent It takes an {\tt IO} action, and a predicate.  The predicate
servers two purposes.  It selects the type of the expected exception,
and constraints the value.  Here is an example:

@@

\noindent And it can be used with predicates from {\tt
System.IO.Error}, to require specific {\tt IOException}, e.g.  with
{\tt isPermissionError}:

\begin{quote}
\small
\begin{verbatim}
launchMissiles `shouldThrow` isPermissionError
\end{verbatim}
\end{quote}

@@

\noindent Which can be used like so:

>>>>

\noindent Or we may expect that a value should satisfy some
predicate.

@@

HUnit does not provide a convenient mechanism to state that an action
should throw an exception.  So we propose a combinator for that.

@@

\noindent It takes an {\tt IO} action, and a predicate.  The predicate
servers two purposes.  It selects the type of the expected exception,
and constrains the value.  Here is an example:

@@

%\noindent And it can be used with predicates from {\tt
%System.IO.Error}, to require specific {\tt IOException}, e.g.  with
%{\tt isPermissionError}:
%
%\begin{quote}
%\small
%\begin{verbatim}
%launchMissiles `shouldThrow` isPermissionError
%\end{verbatim}
%\end{quote}

@@

\noindent Which can be used like this:
